\huge Platform for Anomaly Detection in Time-Series

### 2018-10-22 article.tex
Second Draft Ready.

@@

\usepackage[backend=biber, style=numeric,autocite=plain,sorting=none]{biblatex}
\addbibresource{bibliography.bib}

@@

In this section we present the anomaly detection platform and it's functionalities.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Workflow}
\label{fig:workflow}
\caption{Workflow of the thing.}
\end{figure}

@@

If such a predicate function is not possible, or doesn't meet the correctness requirements, a more complex approach can be used. Since the time series is generated by a generative process, one could hope to be able to accurately describe the underlying process, and create a model of the system:
$$x_t^* = f(t)$$

@@

An ilustration of this can be seen in Figure \ref{fig:outlier}.

In practice, this is almost never possible. Instead the model will predict the new values based on the old observed values: $f : x^n \rightarrow x^*, n \ge 1$. If $n < |X|$, we use a sliding window approach, where we generate a prediction for the next value based on the actual old values. This is useful if we can model the time series using an auto-regressive model.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Outlier}
\label{fig:outlier}
\caption{The upper graphs shows measured values from a process, and the lower figure is the classification. While the signal stays withing a certain range of the model, represented here by the upper and lower bounds, the signal is considered nominal. Points that are outside this ``band of normality'' are considered anomalies.}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{ChangePoint}
    \label{fig:changepoint}
    \caption{In the top most graph, we can see the observed process. In this case it is a pure sine wave. In the middle graphs we can see the coefficient of the model, which in this case is just a function of it's frequency, since it is enough to perfectly describe the process. We can consider as anomaly either the change point, either all the points where the model is outside some bounds.}
\end{figure}

@@

@@

\section*{Bibliography}

\printbibliography

>>>>

\usepackage{cite}

@@

@@

In this section we present the anomaly detection platform and its functionalities for time-series data.

In Figure \ref{fig:workflow} the envisioned workflow is presented. The user starts by loading in some data that she wishes to analyze. She can now choose to visualize the data using the visualization tools provided by the platform. The user can apply transformations to the dataset either to smooth out the data or in an attempt to improve the classification results. Next, a user can try out a host of anomaly detection algorithms. Each one will have a set parameters. These can be fine tuned to improve the classification quality. This can be measured using classification metrics, such as precision and recall.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Workflow}
\caption{Workflow of the classification process.}
\label{fig:workflow}
\end{figure}

@@

If such a predicate function is not possible, or doesn't meet the correctness requirements, a more complex approach can be used. Since the time-series is generated by a generative process, one could hope to be able to accurately describe the underlying process, and create a model of the system:
$$x_t^* = f(t)$$
where $x_t^*$ is the predicted value of $x$ at time $t$. \\

@@

An ilustration of this can be seen in Figure \ref{fig:outlier}. \\

Other regressive models, that use the past values to predict the new values are also used: $x_t^* = f(x_{t-1}, x_{t-2}, \dots, x_{t-n}), n \ge 1$. If given that the data starts at $t=0$ and $t-n > 0$, we use a sliding window approach, where we generate a prediction for the next value based on the actual old values. This is useful if we can model the time series using an auto-regressive model.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Outlier}
\caption{The upper graphs shows measured values from a process, and the lower figure is the classification. While the signal stays withing a certain range of the model, represented here by the upper and lower bounds, the signal is considered nominal. Points that are outside this ``band of normality'' are considered anomalies.}
\label{fig:outlier}
\end{figure}

@@

Change Point detection focuses on the underlying model of the process. The data is generated by a generative process $f(t, p)$, where $p \in {\rm I\!R}^n$ are the parameters of the model. That process is considered to be the nominal generative process. There is also an error $e(t)$ associated with the process. The error function is usually considered to be white noise.
$$x_t = f(t, p) - e(t)$$

This detection methods focuses on more long term changes compared to regular outlier detection methods. When a change in the system behavior is observed, it is considered an anomalous behavior. In other words, we constantly update the parameters of the process $p_n$, and compare it with the previous parameters $p_{n-1}$. $p_n$ is considered an anomalous behavior if $|p_n - p_{n-1}| > d_p$, where $d_p \in {\rm I\!R}$ is a threshold value.

An example of this is illustrated in Figure \ref{fig:changepoint}.

\begin{figure}
\centering
\includegraphics[width=\textwidth]{ChangePoint}   
\caption{In the top most graph, we can see the observed process. In this case it is a pure sine wave. In the middle graphs we can see the coefficient of the model, which in this case is just a function of it's frequency, since it is enough to perfectly describe the process. We consider as anomaly either the change point, either all the points where the model is outside some bounds.}
\label{fig:changepoint}
\end{figure}

@@

In this section we will perform some experiments on some data, but we have not yet decided what we are going to do.

@@

As a conclusion, we think it is a good idea to pull together all the anomaly detection methods used for time-series into a single platform.

\bibliography{refs} 
\bibliographystyle{ieeetr}
